---
title: "Behavior Pilot v2"
author: "Wanjia Guo"
date: "11/16/2021"
output:
  html_document:
    toc: true
    toc_float: true
    theme: journal
editor_options: 
  chunk_output_type: console
---

```{r include = FALSE}
knitr::opts_chunk$set(echo=FALSE, warning = FALSE)
library(gt)
library(fs)
library(purrr)
library(tidyverse)
theme_set(theme_minimal(15))
```


```{r setup, include=FALSE}

converting_read <- function(curr_path){
  print(curr_path)
  read_csv(curr_path) %>% mutate(sub = as.character(sub))
}

converting_read2 <- function(curr_path){
  print(curr_path)
  read_csv(curr_path) %>% mutate(sub = as.character(sub))
}

# Loading behavioral data
sub_dir = dir_ls(here::here("../study_design/behavioral_code/Monstera_fMRI_testing/data/"))
prescan_behav <- map(sub_dir, dir_ls, glob = '*prescan*_behav*.csv') %>% unlist()
scan_behav <- map(sub_dir, dir_ls, regexp = '(.*)_scan(\\d?\\d)_behav_.*') %>% unlist()
postscan_behav <- map(sub_dir, dir_ls, glob = '*postscan*_behav*.csv') %>% unlist()

prescan_batch <- map_dfr(prescan_behav, converting_read)
scan_batch <- map_dfr(scan_behav, converting_read)
postscan_batch <- map_dfr(postscan_behav, converting_read)
```


## n = `r nrow(prescan_batch)/24`

# QA

```{r}
scan_batch = scan_batch %>% 
  mutate(
  correct = ifelse(resp_obj == destination, 1, 0),
  confidence = ifelse(conf_resp == 6, 1, 0),
  cor_conf = ifelse((resp_obj == destination & 
                       conf_resp== 6), 1, 0))
```

Accuracy per sub during scan phase:

```{r}
scan_batch %>% group_by(sub) %>% summarise(
  m_correct = mean(correct),
  m_conf = mean(confidence),
  m_conf_correct = mean(cor_conf)
) %>% gt()
```

*Excluding subject 05*

*Notice: sub1/3/7 have very low confidence.*

```{r}
prescan_batch = prescan_batch %>% filter(sub != '05')#  & sub != '03'& sub != '01')
scan_batch = scan_batch %>% filter(sub != '05')# & sub != '03' & sub != '01')
postscan_batch = postscan_batch %>% filter(sub != '05')# & sub != '03' & sub != '01')
```


# Prescan analysis

Participant were instructed to answer the expected destination for 3 times during the route: once at Same, once at Overlapping, and once at non-overlapping. They also indicated their confidence towards the choice (sure vs. unsure).

```{r}
prescan_batch = prescan_batch %>% 
  mutate(
  nquestion = rep(c(1, 2, 3), times = nrow(prescan_batch)/3),
  correct = ifelse(resp_obj == destination, 1, 0),
  confidence = ifelse(conf_resp == 6, 1, 0),
  cor_conf = ifelse((resp_obj == destination & 
                       conf_resp== 6), 1, 0))

sub_plot = prescan_batch %>% 
  mutate(round_text = paste0('Round',round)) %>% 
  group_by(sub, nquestion, round_text, round) %>% 
  summarise(m = mean(correct), conf = mean(confidence),
            cor_conf = mean(cor_conf)) 

sub_plot %>% group_by(sub) %>% 
  summarise(correct = mean(m)) %>% 
  inner_join(
    sub_plot %>% group_by(sub) %>% 
    summarise(conf = mean(conf)) %>% 
    arrange(conf)) %>% 
  inner_join(
    sub_plot %>% group_by(sub) %>% 
    summarise(conf_correct = mean(cor_conf))) %>% 
  gt() %>%
  fmt_number(
    columns = starts_with('co'),
    decimals = 3)%>%
  tab_header(title = "Prescan Performance") 

curr_plot = sub_plot %>%
  group_by(round_text, nquestion) %>% 
  summarise(mean = mean(m),
            se = sd(m)/sqrt(n()),
            mean_conf = mean(conf),
            conf_se = sd(conf)/sqrt(n()),
            mean_cor_conf = mean(cor_conf),
            cor_conf_se = sd(cor_conf)/sqrt(n()))


ggplot(curr_plot, aes(x = nquestion, y = mean)) + 
  geom_histogram(stat = "identity")+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), color="red", width=0.1, size=0.5)+
  facet_wrap(~round_text)+
  labs(title = 'Accuracy for pre-scan')
  
ggplot(curr_plot, aes(x = nquestion, y = mean_conf)) + 
  geom_histogram(stat = "identity")+
  geom_errorbar(aes(ymin=mean_conf-conf_se, ymax=mean_conf+conf_se), color="red", width=0.1, size=0.5)+
  facet_wrap(~round_text)+
  labs(title = 'Confidence response for pre-scan')
  #gt() %>% cols_align(align = 'left')

ggplot(curr_plot, aes(x = nquestion, y = mean_cor_conf)) + 
  geom_histogram(stat = "identity")+
  geom_errorbar(aes(ymin=mean_cor_conf-cor_conf_se, ymax=mean_cor_conf+cor_conf_se), color="red", width=0.1, size=0.5)+
  facet_wrap(~round_text)+
  labs(title = 'Confident correct for pre-scan')

sub_plot$round_text = factor(sub_plot$round_text)
```

ANVOA for Accuracy:

```{r}
ez::ezANOVA(
  data = sub_plot,
  wid = sub,
  within = .(round, nquestion),
  dv = m
)
```

ANVOA for Confidence:

```{r}
ez::ezANOVA(
  data = sub_plot,
  wid = sub,
  within = .(round, nquestion),
  dv = conf
)
```

ANVOA for high confidence accuracy:

```{r}
ez::ezANOVA(
  data = sub_plot,
  wid = sub,
  within = .(round, nquestion),
  dv = cor_conf
)
```

t-test for mean (overlapping segment):

```{r}
t.test(sub_plot %>% filter(round == 1 & nquestion == 1) %>% .$m,
       sub_plot %>% filter(round == 2 & nquestion == 1) %>% .$m,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 2) %>% .$m,
       sub_plot %>% filter(round == 2 & nquestion == 2) %>% .$m,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 3) %>% .$m,
       sub_plot %>% filter(round == 2 & nquestion == 3) %>% .$m,
       paired = TRUE)
```

t-test for confidence (overlapping segment):

```{r}
t.test(sub_plot %>% filter(round == 1 & nquestion == 1) %>% .$conf,
       sub_plot %>% filter(round == 2 & nquestion == 1) %>% .$conf,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 2) %>% .$conf,
       sub_plot %>% filter(round == 2 & nquestion == 2) %>% .$conf,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 3) %>% .$conf,
       sub_plot %>% filter(round == 2 & nquestion == 3) %>% .$conf,
       paired = TRUE)
```

t-test for high confidence accuracy (overlapping segment):

```{r}
t.test(sub_plot %>% filter(round == 1 & nquestion == 1) %>% .$cor_conf,
       sub_plot %>% filter(round == 2 & nquestion == 1) %>% .$cor_conf,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 2) %>% .$cor_conf,
       sub_plot %>% filter(round == 2 & nquestion == 2) %>% .$cor_conf,
       paired = TRUE)

t.test(sub_plot %>% filter(round == 1 & nquestion == 3) %>% .$cor_conf,
       sub_plot %>% filter(round == 2 & nquestion == 3) %>% .$cor_conf,
       paired = TRUE)
```


```{r}

route_df <- data.frame(route=rep(c('pair1_east', 
                             'pair2_north', 
                             'pair3_west', 
                             'pair4_south'), each=2),
                 destination=c('bench', 'bikerack', 
                               'pole', 'window', 
                               'bush', 'pergola', 
                               'entrance', 'map'),
                 competitor=c('bikerack','bench',
                               'window', 'pole', 
                               'pergola', 'bush', 
                               'map', 'entrance'))

prescan_batch_competitor = prescan_batch %>% 
  inner_join(route_df, by = c('route', 'destination')) %>% 
  mutate(type = ifelse(resp_obj == destination, 'target',
                       ifelse(resp_obj == competitor, 'competitor',
                              'non-competitor')
                       ))

prescan_batch_competitor %>% 
  mutate(sub = as.factor(sub),
         nquestion = as.factor(nquestion),
         round = as.factor(round),
         type = as.factor(type)) %>% 
  count(sub, nquestion, round, type, .drop=FALSE) %>% 
  mutate(percentage = n / 4) %>% 
  group_by(nquestion, round, type) %>% 
  summarise(m = mean(percentage),
            se = sd(percentage)/sqrt(n()),
            n = n()) %>% 
  mutate(round_text = paste0('Round',round)) %>% 
  ggplot(aes(x = nquestion, y = m, fill = type)) + 
  geom_histogram(stat = "identity", position = 'dodge')+
  geom_errorbar(aes(ymin=m-se, ymax=m+se), color="black", width=0.1, size=0.5,
                position = position_dodge(0.9))+
  facet_wrap(~round_text)+
  theme(legend.position = 'bottom')+
  labs(title = 'Correct for pre-scan,\nspearated by answer type',
       y = 'percentage')+
  colorblindr::scale_fill_OkabeIto()
  
```


# Scan analysis

Accuracy per round:

```{r}

curr_plot = scan_batch %>% group_by(round, sub) %>% summarise(
  m_correct = mean(correct),
  m_conf_correct = mean(cor_conf)
) %>%
  group_by(round) %>% summarise(
  se_correct = sd(m_correct)/sqrt(n()),
  m_correct = mean(m_correct),
  se_conf_correct = sd(m_conf_correct)/sqrt(n()),
  m_conf_correct = mean(m_conf_correct)) %>% 
  pivot_longer(cols = starts_with('m_'),
                   names_to = 'type',
                   values_to = 'accuracy') %>% 
  pivot_longer(cols = starts_with('se_'),
                   names_to = 'se_type',
                   values_to = 'se') %>% 
  separate(type, c("A", "type", "C"), sep = '_') %>% 
  mutate(type = ifelse(type == 'conf', 'conf_correct', type)) %>% 
  select(-c(A, C)) %>% 
  separate(se_type, c("A", "se_type", "C"), sep = '_') %>% 
  mutate(se_type = ifelse(se_type == 'conf', 'conf_correct', se_type)) %>% 
  select(-c(A, C)) %>% 
  filter(type == se_type)

ggplot(curr_plot, aes(x = round, y = accuracy, color = type)) +
  geom_line(size = 1)+
  geom_errorbar(aes(ymin=accuracy-se, ymax=ifelse(accuracy+se>1, 1, accuracy+se)), width=0.1, size=0.5)+
  theme(legend.position = 'bottom')+
  colorblindr::scale_color_OkabeIto()
```

Distribution of picture index:

```{r fig.width=10, fig.height=12}

curr_plot = scan_batch %>% group_by(npic, route, destination) %>% summarise(
  m_correct = mean(correct),
  m_conf_correct = mean(cor_conf)) %>% 
  mutate(route = factor(route, levels = c('pair1_east','pair3_west','pair2_north','pair4_south')),
         destination = factor(destination, levels = c('bench','bikerack','bush','pergola',
                                   'pole','window','entrance','map')))

ggplot(curr_plot, aes(x = npic, y = m_correct)) + 
  geom_line()+
  facet_wrap(destination~route, ncol = 2)+
  labs(title = 'Accuracy over picture')

ggplot(curr_plot, aes(x = npic, y = m_conf_correct)) + 
  geom_line()+
  facet_wrap(destination~route, ncol = 2)+
  labs(title = 'High confidence accuracy over picture')

```


# Postscan analysis

```{r}
postscan_batch = postscan_batch %>% 
  mutate(
  correct = ifelse(post_first_resp_obj == destination, 1, 0))

postscan_batch %>% group_by(sub) %>% 
  summarise(m = mean(correct)) %>% 
  gt() %>%
  tab_header(
    title = "Mean accuracy per subject"
  )

postscan_batch %>% group_by(sub) %>% 
  summarise(m = mean(correct)) %>% 
  summarise(m = mean(m))
```


```{r fig.width=16, fig.height=10}
postscan_batch %>% 
  filter(correct == 1) %>%
  mutate(route = factor(route, levels = c('pair1_east','pair3_west','pair2_north','pair4_south')),
         destination = factor(destination, levels = c('bench','bikerack','bush','pergola','pole','window','entrance','map'))) %>% 
  ggplot(aes(x = npic, fill = sub)) +
  geom_histogram() +
  labs(title = 'Picture index for correct trials')+
  facet_wrap(destination~route, ncol = 2)
```


```{r}
postscan_batch %>% 
  filter(correct == 0) %>%
  mutate(route = factor(route, levels = c('pair1_east','pair3_west','pair2_north','pair4_south')),
         destination = factor(destination, levels = c('bench','bikerack','bush','pergola','pole','window','entrance','map'))) %>% 
  ggplot(aes(x = npic, fill = sub)) +
  geom_histogram() +
  labs(title = 'Picture index for incorrect trials')+
  facet_wrap(destination~route, ncol = 2)
```


