---
title: "R&D session"
author: "Wanjia Guo"
date: "1/18/2022"
output: html_document
---

```{r include = FALSE}
knitr::opts_chunk$set(echo=FALSE, warning = FALSE)
library(gt)
library(fs)
library(purrr)
library(tidyverse)
theme_set(theme_minimal(15))
```


```{r setup, include=FALSE}

converting_read <- function(curr_path){
  print(curr_path)
  read_csv(curr_path)
}

# Loading event file
sub_dir = dir_ls(here::here("event_files/"))
event_df <- map_dfr(sub_dir, converting_read, .id = "iteration")

event_df = event_df %>% mutate(
      sub = str_replace_all(
        iteration, 
        "^.*sub-MONSTERA(\\d?\\d).+", 
        "\\1"
    ),
    run = str_replace_all(
        iteration, 
        "^.*_run-(\\d?\\d)_events.tsv", 
        "\\1"
    )
  )

# Loading fMRI data
sub_dir = dir_ls(here::here("fmri_voxels/"))
df <- map(sub_dir, dir_ls, glob = '*.csv') %>% unlist()

batch_df <- map_dfr(df, converting_read, .id = "iteration")
  
batch_df = batch_df %>% mutate(
      sub = str_replace_all(
        iteration, 
        "^.*sub-MONSTERA(\\d?\\d).+", 
        "\\1"
    ),
    run = str_replace_all(
        iteration, 
        "^.*run-(\\d?\\d).csv", 
        "\\1"
    )
  )
```

```{r}
event_df = event_df %>% select(-iteration)
batch_df= batch_df %>% select(-iteration)
```

### sub00:

6: 1 partial fourier, 4 multiband accelerator

7: 1 partial fourier, 3 multiband accelerator

8: 0.875 partial fourier, 6 multiband accelerator (Similar to Aitken & Kok).

### sub01:

7: partial Fourier of 6/8 with a TE of 33ms.

8: 6/8 partial Fourier with a shorter TE of 27ms (Jolinda suggested this might be better). Longer rise time. 

9: also 27 TE. Different from the previous one with a shorter rise time.

10: same as the run 8 of sub00 but with more slices (60 now, 45 before). partial Fourier of 7/8 with a slightly longer TE of 36ms.


## Mean and SD of activity for each round for all voxels in PPA.

### Including catch trials

Both mean and SD are calculated for each trial first, then take mean within each scan session.

```{r}

batch_df_long = batch_df %>% 
  pivot_longer(!c(sub, run), names_to = 'trial', values_to = 'activity')
  
df_plot = batch_df_long %>% group_by(sub, run, trial) %>% 
  summarise(tmp_m = mean(activity),
            tmp_sd = sd(activity)) %>% 
  mutate(run = as.numeric(run)) %>% 
  group_by(sub, run) %>% 
  summarise(m = mean(tmp_m),
            sd = mean(tmp_sd),
            m_sd = m/sd)

ggplot(df_plot, aes(x = run, y = m)) + geom_bar(stat = 'identity') + 
  #geom_errorbar(aes(ymin=m-sd, ymax=m+sd), width=0.1, size=0.5)+
  facet_wrap(~sub) + 
  labs(title = "Mean activity for all voxels in PPA.")

ggplot(df_plot, aes(x = run, y = sd)) + geom_bar(stat = 'identity') + 
  #geom_errorbar(aes(ymin=m-sd, ymax=m+sd), width=0.1, size=0.5)+
  facet_wrap(~sub) + 
  labs(title = "Mean SD for all voxels in PPA.")

ggplot(df_plot, aes(x = run, y = m_sd)) + geom_bar(stat = 'identity') + 
  #geom_errorbar(aes(ymin=m-sd, ymax=m+sd), width=0.1, size=0.5)+
  facet_wrap(~sub) + 
  labs(title = "Mean/SD for all voxels in PPA.")

```

### Remove catch trials

```{r}

total_df = full_join(batch_df_long %>% 
            mutate(trial = as.numeric(trial)), 
          event_df)

remove_catch_df = total_df %>% filter(duration == 24)

df_plot = remove_catch_df %>% group_by(sub, run, trial) %>% 
  summarise(tmp_m = mean(activity),
            tmp_sd = sd(activity)) %>% 
  mutate(run = as.numeric(run)) %>% 
  group_by(sub, run) %>% 
  summarise(m = mean(tmp_m),
            sd = mean(tmp_sd),
            m_sd = m/sd)

ggplot(df_plot, aes(x = run, y = m)) + geom_bar(stat = 'identity') + 
  facet_wrap(~sub) + 
  labs(title = "Mean activity for all voxels in PPA.")

ggplot(df_plot, aes(x = run, y = sd)) + geom_bar(stat = 'identity') + 
  facet_wrap(~sub) + 
  labs(title = "Mean SD for all voxels in PPA.")

ggplot(df_plot, aes(x = run, y = m_sd)) + geom_bar(stat = 'identity') + 
  facet_wrap(~sub) + 
  labs(title = "Mean/SD for all voxels in PPA.")
```

